---
title: "Gov_officials"
output: html_document
---

```{r setup, include=FALSE}
require(dplyr)
library(data.table)
library(dummies)
require(anytime)
require(lubridate)
require(mclust)
require(arm)
library(e1071)
library(caret)

```

## R Markdown
read data
```{r cars}
background1 <- read.csv("background1.csv", header=T, na.strings=c("","NA"))
background2 <- read.csv("background2.csv",header=T, na.strings=c("","NA"))
backgroundNo2 <- read.csv("no_background2.csv")
area_code <- read.csv("area_code.csv")
School_code <- read.csv("SchoolCode.csv")
job_title <- read.csv("job_Title_code.csv")
```


clean data and convert var to binary
党派信息 ?= time to join the Party?
```{r}
background1$X <- NULL
names(background1)[4] <- '生日'


#recode
table(background1$最高学历) 
background1$最高学历<- recode(background1$最高学历, 不详 = "No_inf", 专科 = "diploma", 中专 = "highS_diploma",初中 = "secondary", 博士 = "phd",博士后 = "posdoc",本科 = "undergrad",硕士 = "master",高中 = "secondary2")
#convert NA to 0
background1$最高学历[is.na(background1$最高学历)] <- "No_inf"

table(background1$现状) 
background1$现状<- recode(background1$现状, 不详= "No_inf",在职 = "in_service", 死亡 = "dead",立案查处 = "investigation", 退休 = "retired" )
background1$现状 <- as.character(background1$现状)
#partical match this one due to special symbol '/' in the string
background1[grepl("降", background1$现状), "现状"] <- "dispose"

table(background1$军队) # 1= Yes 
background1$军队[is.na(background1$军队)] <- 'no_inf'
background1$军队<- recode(background1$军队,  "0" = "No", "1" = "Yes")

table(background1$开除党籍) #not sure what happened to NA, I'll convert them to 0
background1$开除党籍 <- as.character(background1$开除党籍)
background1$开除党籍[is.na(background1$开除党籍)] <- 'no_info'
background1$开除党籍<- recode(background1$开除党籍, 否= "No",是 = "Yes")

table(background1$查处.罢黜原因)
background1$查处.罢黜原因<- recode(background1$查处.罢黜原因, 其他= "other", 生活作风问题 = "scandal", 责任事故 = "negligence",贪污腐败 = "curruption", 违纪 = "breaking_rules" )

table(background1$是否复出)
background1$是否复出<- recode(background1$是否复出, 否= "No", 是 = "Yes")

table(background1$是否起诉)
background1$是否起诉<- recode(background1$是否起诉, 否= "No", 是 = "Yes")

table(background1$性别)
background1$性别<- recode(background1$性别, 女= "Female", 男 = "Male")

table(background2$是否全国性组织)
background2$是否全国性组织<- recode(background2$是否全国性组织, 否= "No", 是 = "Yes")

table(background2$是否中央派出)
background2$是否中央派出<- recode(background2$是否中央派出, 否= "No", 是 = "Yes")


```

#background1
let's cluster the cases and see if there's any pattern
```{r}
#convert factors to dummy
clean_data<-dummy.data.frame(background1,names=c('最高学历'),sep='_')
clean_data<-dummy.data.frame(clean_data,names=c('现状'),sep='_')
clean_data<-dummy.data.frame(clean_data,names=c('开除党籍'),sep='_')
clean_data<-dummy.data.frame(clean_data,names=c('查处.罢黜原因'),sep='_')
clean_data<-dummy.data.frame(clean_data,names=c('开除党籍'),sep='_')
clean_data<-dummy.data.frame(clean_data,names=c('是否复出'),sep='_')
clean_data<-dummy.data.frame(clean_data,names=c('是否全国性组织'),sep='_')
clean_data<-dummy.data.frame(clean_data,names=c('是否中央派出'),sep='_')
clean_data<-dummy.data.frame(clean_data,names=c('是否起诉'),sep='_')
clean_data<-dummy.data.frame(clean_data,names=c('性别'),sep='_')
clean_data<-dummy.data.frame(clean_data,names=c('军队'),sep='_')

#add age
clean_data$today <- as.Date("2018-09-23")
clean_data$age <- anytime(clean_data$today) - anytime(clean_data$生日)
clean_data$age <- round(as.numeric(clean_data$age/360), digits= 0)

#add how many years they have joined the party
clean_data$join_p <- anytime(clean_data$today) - anytime(clean_data$党派信息)
clean_data$join_p <- round(as.numeric(clean_data$join_p/360), digits= 0)

#age when they join the party
clean_data$join_age <- anytime(clean_data$党派信息) - anytime(clean_data$生日) 
clean_data$join_age <- round(as.numeric(clean_data$join_age/3600/24/360), digits= 0)
```

#background2
calculate start - end (How long have they been in the a gov official in the party?)
```{r}
options(digits.secs=6)
Sys.setenv(TZ=anytime:::getTZ()) 
background2$time_diff <- anytime(background2$终止时间..YYYY.MM.DD..) - anytime(background2$起始时间.YYYY.MM.DD.)
background2$time_diff <- round(background2$time_diff/3600/24/360, digits= 2)
```




#add how many times they work in central？ also get the most freq province of each person 
基本大类别
```{r}
table(background2$基本大类别)
background2$基本大类别<- recode(background2$基本大类别, 中央企业= "0", 人大 = "1", 党委 = "2",共青团 = "3",  其他 = "4", 军队 = "5", 地方企业 = "6", 基层组织 = "7", 学校 = "8",政协 = "9",政府_国务院 = "10",民主党派 = "11",法院_检察院 = "12",行业协会_人民团体 = "13" )
clean_data2<-dummy.data.frame(background2,names=c('基本大类别'),sep='_')
```

地方一级关键词
```{r}
table(clean_data2$地方一级关键词)
clean_data2$地方一级关键词<- recode(clean_data2$地方一级关键词, 上海市= "0", 不详 = "1", 中央 = "2",乍得 = "3",  云南省 = "4", 伊朗 = "3", 几内亚 = "3",加纳 = "3", 肯尼亚 = "3", 南斯拉夫 = "3",卢旺达 = "3",坦桑尼亚 = "3",埃及 = "3", 巴基斯坦 = "3",朝鲜 = "3",津巴布韦 = "3", 莱索托 = "3",乍得 = "3",俄罗斯联邦 = "5", 苏联 = "5",内蒙古自治区 = "6",加拿大 = "7", 奥地利 = "7",意大利 = "7",挪威 = "7",  日本 = "7",比利时 = "7",法国 = "7",波兰 = "7",澳大利亚 = "7",爱尔兰 = "7",新加坡 = "7",捷克斯洛伐克 = "7",瑞典 = "7",美国 = "7",英国 = "7",荷兰 = "7",北京市 = "8",吉林省 = "9",四川省 = "10",天津市 = "11", 宁夏回族自治区 = "12",安徽省 = "13", 山东省 = "14",山西省 = "15",广东省 = "16",广西壮族自治区 = "17",新疆维吾尔自治区 = "18",晋冀鲁豫边区 = "19",江苏省 = "20", 江西省 = "21",河北省 = "22",河南省 = "23",浙江省 = "24",海南省 = "25",湖北省 = "26",湖南省 = "27",澳门特别行政区 = "28",  香港特别行政区 = "28",甘肃省 = "29",福建省 = "30",西藏自治区 = "31", 贵州省 = "32",辽宁省 = "33",重庆市 = "34",陕西省 = "35",青海省 = "36", 黑龙江省 = "36", 晋察冀边区 = "37", 黑龙江省 = "38")
clean_data2[grepl("德国", clean_data2$地方一级关键词), "地方一级关键词"] <- "7"
clean_data2[grepl("苏南", clean_data2$地方一级关键词), "地方一级关键词"] <- "5"


clean_data2$地方一级关键词 <- factor(clean_data2$地方一级关键词)
table(clean_data2 $地方一级关键词)

#convert to dummy
clean_data2<-dummy.data.frame(clean_data2,names=c('地方一级关键词'),sep='_')
```



```{r}
table(clean_data2$级别)
#convert to dummy
clean_data2$级别<- recode(clean_data2$级别, 副厅= "deputy_director", 副国 = "deputy_leader", 副处 = "deputy_dept",副部 = "vice_minister",  小于副处 = "less_dept", 无级别 = "no_rank", 正厅 = "director",正国 = "national_leader", 正处 = "dept", 正部 = "minister")
clean_data2<-dummy.data.frame(clean_data2,names=c('级别'),sep='_')
```

sum the position, place and institute for each case
```{r}
cols <- c(2,6:7, 9:47, 53:66, 73:82, 86)
fea2 <- clean_data2[,cols]
fea3 <- aggregate(. ~ 姓名, fea2, sum)

```

merge with background1
```{r}
#get background1
cols <- c(1:3, 9:17, 19:35,37:39,43:44,55:57)
fea4 <- clean_data[,cols]
#merge
fea <- merge(fea3, fea4, by = '姓名')

```

let's cluster the data and see the patterns
```{r}
#convert all the var to numbers, replace NA with mean
fea$join_age <- ifelse(is.na(fea$join_age), mean(fea$join_age , na.rm=TRUE), fea$join_age)
fea$join_p <- ifelse(is.na(fea$join_p), mean(fea$join_p , na.rm=TRUE), fea$join_p)
fea$age <- ifelse(is.na(fea$age), mean(fea$age, na.rm=TRUE), fea$age)

data2 <- as.data.frame(lapply(fea[ ,2:103], as.numeric))
```

select features for clustering： ranking, time joining party, age when joining party, positions
```{r}
# ranking, time joining party, age when joining party, positions
cols <- c(56:65,100:102,66,1:2)
data <- data2[,cols]
#cluster
#data <- data.frame(apply(data,2,rescale))
BIC <- mclustBIC(scale(data))
plot(BIC)
```

```{r}
summary(BIC)
mod1 <- Mclust(data, x = BIC)
s <- summary(mod1, parameters = TRUE)
s
```

select features for clustering： ranking, time joining party, age when joining party, positions
```{r}
#location
cols <- c(3:41)
data <- data2[,cols]

#PCA
prin_comp <- prcomp(data, scale. = T)
prin_comp$rotation
biplot(prin_comp, scale = 0)

```

frequency of changing positions.  does freq related to edu? ranking?
```{r}
#should add frequency of changing position  freq/time_diff   how often do they change a position
freq_change_pos <- data.frame(table(background2$姓名))
freq_all <- merge(freq_change_pos,fea, by.x = "Var1", by.y = "姓名")
#how many years dp they get to change a postion?
freq_all$freq_change_pos_nor <- freq_all$time_diff/freq_all$Freq

#frequency of workin in central
central <- background2 %>% 
  group_by(姓名) %>% 
  filter(., 地方一级关键词 == "中央")

central_freq <- data.frame(table(central$姓名))
colnames(central_freq) <- c('Var1','central_freq')
freq_all <- merge(central_freq,freq_all, by = "Var1")

```

Let's do the cluster again adding the frequency of working in central and frequency of changing positions
```{r}
# ranking, time joining party, age when joining party, positions
cols <- c(2:5, 59:69, 103:106 )
data <- freq_all[,cols]
#cluster
#data <- data.frame(apply(data,2,rescale))
BIC <- mclustBIC(scale(data))
plot(BIC)
```

```{r}
summary(BIC)
mod1 <- Mclust(data, x = BIC)
s <- summary(mod1, parameters = TRUE)
#shows means of each group
s[11]
```

Let's do a regression

```{r}
#recode ranking here we recode no_ranking = 1, ranked = 0
recode_r <- background2[, c(2,22)]
recode_r$级别<- recode(recode_r$级别, 副厅= 9, 副国 = 2, 副处 = 6,副部 = 4,  小于副处 = 7, 无级别 = 10, 正厅 = 8,正国 = 1, 正处 = 5, 正部 = 4)
#clean_data2<-dummy.data.frame(clean_data2,names=c('级别'),sep='_')
#select the highest ranking of each person
highest_rank <- aggregate(级别 ~ 姓名, data = recode_r, min)
#merge with features
all <- merge(highest_rank,freq_all, by.x = '姓名', by.y = 'Var1')

#regress the highest ranking 
cols <- c(2:6, 70, 104:107 )
reg_fea <- all[cols]
l <- lm(formula = 级别 ~ ., data = reg_fea)
summary(l)
```



let's try svm to predit those work in the province or above level
remove age, because regression shows it's not predictive
```{r}
highest_rank$级别<- recode(highest_rank$级别,  "1" = 1, "2" = 1, "3" = 1,  "7" = 0, "10" = 0, "8" = 0, "9" = 0, "4" = 1, "5" = 0, "6" = 0)
#select the highest ranking of each person
table(highest_rank$级别)
#merge with features
all2 <- merge(highest_rank,freq_all, by.x = '姓名', by.y = 'Var1')


#svm predict highest ranking 
cols <- c(2:6, 70, 104:107 )
svm_fea <- all2[cols]


set.seed(123)
smp_size <- floor(0.70 * nrow(svm_fea))
train_ind <- sample(seq_len(nrow(svm_fea)), size = smp_size)
train <- svm_fea[train_ind, ]
test <- svm_fea[-train_ind, ]

#Fit a model. The function syntax is very similar to lm function
model_svm <- svm(as.factor(级别) ~ . , train)
#Use the predictions on the data
pred <- predict(model_svm, test)

y <- as.factor(test$级别)
predictions <- pred

precision <- posPredValue(predictions, y, positive="1")
recall <- sensitivity(predictions, y, positive="1")

#78% accurate
(2 * precision  * recall) / (precision + recall)
table(y,predictions)
```

